\documentclass[margin,line]{resume}
\usepackage[hidelinks]{hyperref}
\setlength{\textheight}{9.7in}

\begin{document}
\name{\Large Brenden Matthews}
\begin{resume}

    \section{\mysidestyle Contact\\Information}

    Phone: \emph{contact me}                  \hfill
    Email: \href{mailto:brenden@brndn.io}{brenden@brndn.io}                   \hfill

    \vspace{3mm}

    \section{\mysidestyle Published\\Works}

    \textbf{Code Like a Pro in Rust}, to be published by Manning Publications,
    estimated early 2023.

    \vspace{3mm}

    \section{\mysidestyle Public\\Speaking}

    Have given numerous talks on my work at conferences and private engagements,
    including but not limited to \textbf{All Things Open}, \textbf{QCon},
    \textbf{LinuxCon}, \textbf{ContainerCon}, and \textbf{MesosCon}.
    
    \vspace{3mm}

    \section{\mysidestyle Open\\Source}

    Contributed to hundreds of open source projects, member of the Apache
    Software Foundation, and have created a number of popular projects with a
    few highlighted below:

    \href{https://github.com/brndnmtthws/conky}{\textbf{Conky}}, C and C++ \hfill \textbf{5600+ GitHub stars}\\
    Endlessly configurable system monitor utility for UNIX systems.

    \href{https://github.com/brndnmtthws/thetagang}{\textbf{thetagang}}, Python \hfill \textbf{1500+ GitHub stars}\\
    Equity options trading tool for profiting from theta decay. Designed for use
    with IBKR.

    \href{https://github.com/brndnmtthws/dryoc}{\textbf{dryoc}}, Rust \hfill \textbf{130+ GitHub stars}\\
    High quality pure-Rust general purpose cryptography library compatible with
    libsodium.  Features generic hash functions suitable for cryptography,
    protected memory, zeroization, and SIMD.

    \vspace{3mm}

    \section{\mysidestyle Professional\\Experience}

    \textbf{Multiple Companies}, USA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Founder, CEO} \hfill \textbf{April 2019 -- present}\\
    Founded multiple small software startups in different sectors. Mostly SaaS,
    self-service and either pay-as-you-go or subscription based.

    \textbf{Braze, Inc.}, New York, NY \vspace{2mm}\\\vspace{1mm}%
    \textsl{Engineering} \hfill \textbf{Oct 2018 -- April 2019}\\
    Building infrastructure with Kubernetes.

    \textbf{Citadel LLC}, New York, NY \vspace{2mm}\\\vspace{1mm}%
    \textsl{Engineering} \hfill \textbf{Oct 2017 -- Jun 2018}\\
    Joined the platform engineering group as part of the data engineering
    team to build out Citadel's data platform technology. Primarily working
    with tools that integrate on-prem and cloud (AWS and GCE) data
    infrastructure.

    \textbf{Mesosphere, Inc.}, San Francisco, CA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Solutions} \hfill \textbf{Jan 2015 -- Feb 2017}\\
    Early Mesosphere employee, was an integral part of founding the company.
    Worked on multiple customer engagements, acting in both pre-sales and
    post-sales positions.

    \begin{itemize}
    \item Built cloud migration plans for enterprise customers
    \item Lead and lectured week-long in-depth onsite training sessions
    \item Advising senior management on container technologies
    \item Lectured and gave talks at several meetups and conferences
    \item Contributed to various engineering efforts
    \item Published several original blog posts
    \item Built and maintained marathon-lb, the canonical load balancing and
     service discovery tool for Marathon and DC/OS
    \item Customers were primarily enterprise users, including financial,
     telecom, and tech companies
    \end{itemize}

    \textbf{Airbnb, Inc.}, San Francisco, CA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Engineering} \hfill \textbf{Feb 2013 -- Jan 2015}\\
    Early employee at Airbnb. Joined the Data Infrastructure team to help
    Airbnb scale to support the massive growth of the company, and meet the
    company's needs for managing a large, growing data warehouse. Worked
    directly with teams all across the company to help meet their data needs,
    and build out a rich set of data tooling.

    \begin{itemize}
    \item Built next generation of data infrastructure utilizing open source
     tools such as Mesos, Hadoop, HDFS, Chronos, and Storm
    \item Contributed code to several projects, including: Mesos, Hadoop,
     Storm, Spark, Presto, Chronos, Marathon, and others
    \end{itemize}

    \textbf{Newfield Wireless, Inc.}, Berkeley, CA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Engineering} \hfill \textbf{Sept 2009 -- Nov 2012}\\
    Leveraged 3GPP layer 3 expertise to build a UMTS network data parser and
    indexer. Designed and implemented the first suite of real-time 3GPP LTE
    capture/parsing tools.

    \begin{itemize}
    \item Created a customized database solution with integrated flexible query language for accessing millions of streaming records in real time.
    \item Designed and implemented asynchronous communication library with feature set similar to ZeroMQ, with C++ and Python interfaces.
    \item Designed and implemented a reporting library for generating key performance indicators from vast quantities of raw data, leveraging previously mentioned customized database.
    \item Introduced new development and debugging methodologies to the team which significantly improved the pace of development and quality of deliverables.
    \item Assisted junior and senior developers on all aspects of software engineering.
    \item Oversaw design and implementation of schema-based XML software specifications.
    \end{itemize}

    \textbf{Real Time Measurements, Inc.}, Calgary, AB \vspace{2mm}\\\vspace{1mm}%
    \textsl{Engineering} \hfill \textbf{2003 -- 2009}\\

    \begin{itemize}
    \item Developed end user applications, web services, and embedded software.
    \item Involved in strategic planning, performance and productivity improvement, organizational design, e-commerce, new media and Internet promotion.
    \item Planned, participated, and coordinated team building exercises while demonstrating strong leadership skills.
    \item Configured and managed servers, automated backup systems, and provided support for customers as well as in-house support.
    \item Leveraged new technologies to enhance our product-to-customer experience in a timely and cost effective fashion.
    \item Implemented cost reduction IT strategy to make use of existing infrastructure instead of requiring further equipment purchases.
    \end{itemize}

    \vspace{3mm}
    
    \section{\mysidestyle Programming\\Experience}

    \emph{Languages:} Rust, C, C++, Python, Ruby, Bash, Go, Java, Scala, Kotlin, \LaTeX \\
    \emph{Data Technology:} Kafka, Cassandra, Redis, PostgreSQL, ElasticSearch/Lucene,
     MySQL, Hadoop, Hive, Presto, RedShift, BigQuery, SQS, EMR, RDS

\end{resume}
\end{document}
